---
title: "Template"
author: "Benjamin Vittrant"
format: 
  html: 
   toc: true
   code-fold: true
   number-sections: true
   number-depth: 2
   anchor-sections: true
   smooth-scroll: true
editor: visual
license: "Copyright Benjamin Vittrant, 2022. All Rights Reserved. The diffusion, reuse or distribution of this document is not allowed."
bibliography: references.bib
---

# Introduction

## Context

## Objectives

# Code set-up

## Clean

```{r, message=F, warning=F}
rm(list = ls(all.names = TRUE))
```

## Packages

```{r, message=F, warning=F}
library(ggsci)
```

## Colors

We define color palette from the *ggsci* [@xiao__aut_ggsci_2023] that recreate color from scientific publication.

```{r}
discrete_ggsci_npg = list(scale_color_npg(), scale_fill_npg())
continuous_ggsci_npg = list(scale_fill_material("light-blue"))
palette = "Paired"
```

# Data collection and preprocessing

# Feature engineering

# Exploration

## Distribution


```{r, message=F, warning=F}

```


The distribution can also be checked using a correlogram where feature distribution is the diagonal part. This graph is created from the *GGally* [@schloerke_ggally_2021] library which extend the ggplot 2 capabilities. You need to reduce matrix input or can take a lot of time nad the plot can be unreadable if you have to much features.

```{r, message=F, warning=F}

```


## Summary statistics

For the summary statistics I used the package from *rstatix* [@kassambara_rstatix_2023] function.

```{r, message=F, warning=F}

```


## Correlation

For the correlation analysis I used the pacakge *polycor* [@fox_polycor_2022, @noauthor_polychoric_2023] which is based on polychoric and polyserial correlation [@drasgow_polychoric_2006].

```{r, message=F, warning=F}

```

## Mutual information

## Heatmap

To plot the heat map I used the unbelieveable package *complex heatmap* [@gu_complex_2016, @gu_complex_2022]. All the doc is availabel on the [github page](https://jokergoo.github.io/ComplexHeatmap-reference/book/index.html).

# Model selection and training

# Model evaluation

# Conlcusion

# Discussion

# Conclusion/Futur work

### References

::: {#refs}
:::
